### 2018-04-11 paper/overview.tex
more work on overview

% include code of running example and some figure:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.26\textwidth] %
    { \caption{\cc{dblAbs}: an example hierarchical program.} %
      \label{fig:multicall-code} }
    { \input{code/dblAbs.java} }
    %
    \ffigbox[.7\textwidth] %
    {\caption{$\mcchc$ shown as a directed hypergraph.
        % 
        Each relational predicate is depicted as a graph node
        while each clause is represented by a hyperedge.
        Each hyperedge is labelled by the fact in the corresponding CHC\@.
        Each node has a valid corresponding interpretation,
        written in braces.
      } %
      \label{fig:ex-graph} }
    % { \includegraphics[width=\linewidth]{fig/ex-deps.pdf} }
      {\input{fig/example}}
  \end{floatrow}
\end{figure}
% walk through code of running example:
%
\cc{dblAbs} is a small procedure that doubles the absolute value of
its input and stores the result in \cc{res}.
% state the safety problem:
The program also asserts that \cc{res} is greater than or equal to $0$
before exiting.
% talk about solving Horn Clauses:
Verifying this assertion can be reduced to solving a recursion-free
CHC system over a set of uninterpreted predicates that each represents
a control location and procedure name in \cc{dblAbs}.
%
In particular, one such system $\mcchc$ is
%
\begin{align}
\label{chc}
  % semantic constraint of dbl:
\cc{dbl}(\cc{x}, \cc{d}) &\gets \cc{d} = 2 * \cc{x} \\
  % semantic constraint of line 3:
  \cc{L}_4(\cc{n}, \cc{abs}) &\gets  \cc{abs} = 0 \\
  % semantic constraint of line 5 (then branch)
  \cc{L}_6(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} \ge 0 \\
  % semantic constraint of line 6 (else branch)
  \cc{L}_8(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} < 0 \\
  % assign branch
  \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_6(\cc{n},\cc{abs}) \land \cc{abs'} = \cc{n} \\
   \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_8(\cc{n},\cc{abs}) \land \cc{abs'} = -\cc{n} \\
  % semantic constraint of main procedure:
   \cc{main}(\cc{n},\cc{res}) &\gets \cc{L}_9(\cc{n}, \cc{abs'}) \land
                                     \cc{dbl}(\cc{x}, \cc{d})
    \land \cc{abs'} = \cc{x} \land \cc{res} = \cc{d} \\
  %
    \bot &\gets \cc{main}(\cc{n}, \cc{res}) \land \cc{res} < 0 
\end{align}
%
While $\mcchc$ has been presented as the result
of a translation from hierarchical program \cc{dblAbs}, \sys is
purely a solver for CHC systems: it does not require access to the
concrete representation of a program, or for a given CHC system to be
the result of translation from a program at all.

% solving the running example
\subsection{\cc{dblAbs} as a Clause-Dependent Disjoint system}
\label{sec:solve-ex}
% state it is CDD
The recursion-free CHC system $\mcchc$ is a
\emph{Clause-Dependent-Disjoint} (CDD) system.
% state the defn of CDD:
A CDD system is a recursion-free CHC system such that
each clause is dependence disjoint.
A clause is dependence disjoint if no two predicates in the body share
any transitive dependencies (i.e, they have no common predicates) and
there are no two predicates that are the same.
%
The formal definition of CDD and its key properties are given in
\autoref{sec:CDD-defn}.

% give a example
In particular, clause $(7)$ uses both $\cc{L}_9$ and $\cc{dbl}$ in its
body.
%
The transitive dependency of $\cc{L}_9$ is the set
$\{\cc{L}_4,\cc{L}_6,\cc{L}_8\}$, while the transitive dependency of
\cc{dbl} is the empty set.
%
Therefore, their transitive dependencies are disjoint:
$\{\cc{L}_4,\cc{L}_6,\cc{L}_8\} \cap \varnothing = \varnothing$.
If there were a conflict in the transitive dependencies, then $\mcchc$
would not be a CDD system.
%
The formal definition of transitive dependency is given in\QZ{reference}.
%
All other clauses in $\mcchc$ have at most one uninterpreted predicate
in the body, so they are trivially disjoint dependent.
%
Since every rule in $\mcchc$ is disjoint dependent, $\mcchc$ is a CDD
system.
%
The fact that $\mcchc$ is CDD corresponds to the fact that there no
statements executed more than once within one execution path.
\DAH{elaborate}
%

% restate defn of CDD systems:
\sys solves $\mcchc$ directly by issuing a binary interpolation query
for each uninterpreted predicate in topological order.
%
Each uninterpreted predicate $P$ has a valid interpretation which can
be computed by finding the interpolant of two formulas:
\textbf{(1)} the \emph{pre}-formula, constructed from the solutions of
each uninterpreted predicate $P$ directly depends on, constraints in
clauses where $P$ is the head, and boolean indicator variables for
each uninterpreted predicate in $\mcchc$%
\textbf{(2)} the \emph{post}-formula, constructed from
all constraints that occur after $P$ and boolean indicator
variables for each uninterpreted predicate in $\mcchc$.
%

We will walk through the interpolation query for $\cc{L}_9$ by hand.
By the time \sys reaches $\cc{L}_9$ it will already have solutions for
$\cc{L}_4$, $\cc{L}_6$, $\cc{L}_8$. Possible interpretations of these
predicates are shown in \autoref{fig:ex-graph}.
%
\DAH{WORK FROM HERE}
A solution for \cc{L9} can be constructed by interpolating \textbf{(1)}
the \emph{pre}-formula, constructed as solutions generated for \cc{L4}, \cc{L6}
the constraints in clauses (5) and (6) and boolean variables%
\textbf{(2)} the \emph{post}-formula constructed from constraints in
$\mcchc$ that all constraints after \cc{L9}, constraints for \cc{dbl}
and boolean variables.
%
In particular, the \emph{pre}-formula for \cc{L9} is 
\begin{gather}
  ((b_{L_8}\land \cc{abs'}= -\cc{n})
    \lor (b_{L_6} \land \cc{abs}=\cc{n}))
  \land (\neg b_{L_6} \lor \cc{n} \ge 0)
    \land (\neg b_{L_8} \lor \cc{n}<0)
\end{gather}
%
, $b_{L8}$ and $b_{L6}$ are boolean variables corresponding to predicates \cc{L8} and \cc{L6}.
%
The \emph{post}-formula for \cc{L9} is
\begin{gather}
  (b_{main} \land \cc{res'} < 0 )
    \land (\neg b_{main} \lor (b_{dbl} \land \cc{abs'}= \cc{x} \land \cc{res}=\cc{d} ))
  \land (\neg b_{dbl} \lor \cc{d} = 2*\cc{x})
\end{gather}
, $b_{main}$ and $b_{dbl}$ are boolean variables corresponding to
predicates \cc{main} and \cc{dbl}.
%
A detailed and formal description for the procedure of solving a CDD system is given in
\autoref{sec:solve-cdd}.

\subsection{\cc{dblAbs} is not in other system}
\label{sec:not-in}
%
There are three classes of directly solvable systems has been introduced
in previous work(as described in \autoref{sec:intro}).
%
However, $\mcchc$ does not belong to any of these three classes.
%

>>>>

% include code of running example and some figure:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.26\textwidth] %
    { \caption{\cc{dblAbs}: an example hierarchical program.} %
      \label{fig:multicall-code} }
    { \input{code/dblAbs.java} }
    %
    \ffigbox[.7\textwidth] %
    {\caption{$\mcchc$ shown as a directed hypergraph.
        % 
        Each relational predicate is depicted as a graph node
        while each clause is represented by a hyperedge.
        Each hyperedge is labelled by the fact in the corresponding CHC\@.
        Each node has a valid corresponding interpretation,
        written in braces.
      } %
      \label{fig:ex-graph} }
    % { \includegraphics[width=\linewidth]{fig/ex-deps.pdf} }
      {\input{fig/example}}
  \end{floatrow}
\end{figure}
% walk through code of running example:
%
\cc{dblAbs} is a small procedure that doubles the absolute value of
its input and stores the result in \cc{res}.
% state the safety problem:
The program also asserts that \cc{res} is greater than or equal to $0$
before exiting.
% talk about solving Horn Clauses:
Verifying this assertion reduces to solving a recursion-free
CHC system over a set of uninterpreted predicates that represent
the control locations in \cc{dblAbs}.
%
In particular, one such system $\mcchc$ is
%
\begin{align}
\label{chc}
  % semantic constraint of dbl:
\cc{dbl}(\cc{x}, \cc{d}) &\gets \cc{d} = 2 * \cc{x} \\
  % semantic constraint of line 3:
  \cc{L}_4(\cc{n}, \cc{abs}) &\gets  \cc{abs} = 0 \\
  % semantic constraint of line 5 (then branch)
  \cc{L}_6(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} \ge 0 \\
  % semantic constraint of line 6 (else branch)
  \cc{L}_8(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} < 0 \\
  % assign branch
  \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_6(\cc{n},\cc{abs}) \land \cc{abs'} = \cc{n} \\
   \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_8(\cc{n},\cc{abs}) \land \cc{abs'} = -\cc{n} \\
  % semantic constraint of main procedure:
   \cc{main}(\cc{n},\cc{res}) &\gets \cc{L}_9(\cc{n}, \cc{abs'}) \land
                                     \cc{dbl}(\cc{x}, \cc{d})
    \land \cc{abs'} = \cc{x} \land \cc{res} = \cc{d} \\
  %
    \bot &\gets \cc{main}(\cc{n}, \cc{res}) \land \cc{res} < 0 
\end{align}
%
While $\mcchc$ has been presented as the result
of a translation from hierarchical program \cc{dblAbs}, \sys is
purely a solver for CHC systems: it does not require access to the
concrete representation of a program, or for a given CHC system to be
the result of translation from a program at all.

% solving the running example
\subsection{$\mcchc$ as a Clause-Dependent Disjoint System}
\label{sec:solve-ex}
% state it is CDD
The recursion-free CHC system $\mcchc$ is a
\emph{Clause-Dependent-Disjoint} (CDD) system.
% state the defn of CDD:
A CDD system is a recursion-free CHC system such that
the dependencies between predicates in the system obey certain rules.
%
One predicate is directly dependent on another if the second appears
in the body of a clause where the first is the head.
%
Based on this, we say that a clause is dependence disjoint if
\textbf{(1)} no two predicates in the body share any transitive
dependencies on other predicates and \textbf{(2)} no two predicates in
the body are the same.
% give a example
As an example, clause $(7)$ is dependence disjoint. Clause $(7)$ uses
both $\cc{L}_9$ and $\cc{dbl}$ in its body.
%
The transitive dependency of $\cc{L}_9$ is the set
$\{\cc{L}_4,\cc{L}_6,\cc{L}_8\}$, while the transitive dependency of
\cc{dbl} is the empty set.
%
Therefore, their transitive dependencies are disjoint:
$\{\cc{L}_4,\cc{L}_6,\cc{L}_8\} \cap \varnothing = \varnothing$.
%
All other clauses in $\mcchc$ have at most one uninterpreted predicate
in the body, so they are trivially disjoint dependent.
%
When each clause in a CHC system is dependence disjoint, it is a CDD
system. Therefore $\mcchc$ is a CDD system.
%
The fact that $\mcchc$ is CDD corresponds to the fact that there no
statements executed more than once within one execution path.
\DAH{elaborate}
%
The formal definition of CDD and its key properties are given in
\autoref{sec:CDD-defn}.
The formal definition of transitive dependency is given in\QZ{reference}.
%

% restate defn of CDD systems:
\sys solves CDD systems directly by issuing a binary interpolation
query for each uninterpreted predicate in topological order.
%
Each uninterpreted predicate $P$ has a valid interpretation which can
be computed by interpolating
\textbf{(1)} the \emph{pre}-formula, constructed from the solutions of
each uninterpreted predicate $P$ directly depends on and constraints
in clauses where $P$ is the head and
\textbf{(2)} the \emph{post}-formula, constructed from
all clauses where the head transitively depends on $P$.
%

We will walk through the construction of an interpolation query for
$\cc{L}_9$ by hand.  By the time \sys reaches $\cc{L}_9$ it will
already have solutions for $\cc{L}_4$, $\cc{L}_6$, $\cc{L}_8$.
Possible interpretations of these predicates are shown in
\autoref{fig:ex-graph}.
%
A solution for \cc{L9} can be constructed by interpolating \textbf{(1)}
the \emph{pre}-formula, constructed as solutions generated for \cc{L4}, \cc{L6}
the constraints in clauses (5) and (6) and boolean variables%
\textbf{(2)} the \emph{post}-formula constructed from constraints in
$\mcchc$ that all constraints after \cc{L9}, constraints for \cc{dbl}
and boolean variables.
%
In particular, the \emph{pre}-formula for \cc{L9} is 
\begin{gather}
  ((b_{L_8}\land \cc{abs'}= -\cc{n})
    \lor (b_{L_6} \land \cc{abs}=\cc{n}))
  \land (\neg b_{L_6} \lor \cc{n} \ge 0)
    \land (\neg b_{L_8} \lor \cc{n}<0)
\end{gather}
%
, $b_{L8}$ and $b_{L6}$ are boolean variables corresponding to predicates \cc{L8} and \cc{L6}.
%
The \emph{post}-formula for \cc{L9} is
\begin{gather}
  (b_{main} \land \cc{res'} < 0 )
    \land (\neg b_{main} \lor (b_{dbl} \land \cc{abs'}= \cc{x} \land \cc{res}=\cc{d} ))
  \land (\neg b_{dbl} \lor \cc{d} = 2*\cc{x})
\end{gather}
, $b_{main}$ and $b_{dbl}$ are boolean variables corresponding to
predicates \cc{main} and \cc{dbl}.
%
A detailed and formal description for the procedure of solving a CDD system is given in
\autoref{sec:solve-cdd}.

\subsection{$\mcchc$ is not in other system}
\label{sec:not-in}
%
There are three classes of directly solvable systems has been introduced
in previous work(as described in \autoref{sec:intro}).
%
However, $\mcchc$ does not belong to any of these three classes.
%
